---
title: "Mini-Project 2"
author: "Yue Kuang, Alice Mungyu, Margaret Anne Smith"
date: "March 24, 2017"
output: html_document
---


## Loading the data


```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")

library(dplyr)
library(tidyverse)
library(ggplot2)
```

```{r}
total_donation<- contributions%>%
  ##matching contributions with candidate name
  full_join(candidates, by="cand_id")%>%
  
  ##specifying that we wanted donations for the general election
  filter(transaction_pgi=="G")%>%
  
  ##removing contributions with no corresponding candidate names
  filter(!is.na(cand_name))%>%
  
  ##specifying that we wanted donations from only the 2012 election
  filter(cand_election_yr=="2012")%>%
  
  ##specifying that we were only interested in donations to presidential candidates
  filter(cand_office=="P")%>%
  
  ##specifying that we only wanted the Democrat and Republican candidates
  filter((cand_party_affiliation=="DEM")|(cand_party_affiliation=="REP"))
total_donation<- contributions%>%
  ##matching contributions with candidate name
  full_join(candidates, by="cand_id")%>%
  
  ##specifying that we wanted donations for the general election
  filter(transaction_pgi=="G")%>%
  
  ##removing contributions with no corresponding candidate names
  filter(!is.na(cand_name))%>%
  
  ##specifying that we wanted donations from only the 2012 election
  filter(cand_election_yr=="2012")%>%
  
  ##specifying that we were only interested in donations to presidential candidates
  filter(cand_office=="P")%>%
  
  ##specifying that we only wanted the Democrat and Republican candidates
  filter((cand_party_affiliation=="DEM")|(cand_party_affiliation=="REP"))

  ##we wanted our table to contain information for the total amount of money donated from each state to the Democrat or Republican candidate
  group_by(state, cand_party_affiliation)%>%
  
  ##this code calculates the values for the total amount donated
  summarise(sum=sum(transaction_amt))%>%
  
  ##this code allows us to show total amount donated for each party by state - each party becomes a new column
  spread(key = cand_party_affiliation, value =sum)%>%
